The ERJ's 145 ice protection is a thermal heating system type using the engine air bleed as the energy source.

These types of ice protection systems are commonly used in turbo fan engined aircrafts as the ERJ 145 does because of its high energy demand.
In ERJ 145 the bleed air is taken from the 9th and 14th stages of engine's compressor and feeds all the pneumatic system. Part of this air is used to heat the leading edges of wings and horizontal stabilizer and also the engine's air intake lips.

Nowadays the anti-icing system operates with a pressure about 18 $\pm$2 psig and the temperature around 120\celsius on the surfaces, demanding a maximum airflow of 47.8 ppm (pounds per minute) for each wing and 87 ppm for the whole horizontal stab.

The proposal made for the Preliminary Design (PD) phase was to elaborate a AMESim model to validate the system behavior and to include a new control system in order to reduce the airflow demand and then reduce the fuel consumption due to the bleed air.

This control system should measure the temperature of the leading edge and operate the AIV (Anti Ice Valve) to minimize the air mass demand that just works as an ON-OFF system nowadays. It could optimize the energy of the system for each type of ice condition. After a talk with an Embraer employee we found that it was not feasible because would be necessary to change the whole measurement system, once the actual system just indicates that the aircraft is in an icing condition but doesn't indicates what kind of ice is forming on the surfaces and according to this employee, there is no available equipment in the actual market that provides this kind of information. This way, an alternative is to change the AIV operating temperature to reduce the airflow, trying to keep the total energy provided to the leading edges.

Some information about the anti-icing system in flight tests data were provided in order to elaborate the model and to make a comparison between the real system behavior and the model results.
The following table shows some results about ERJ's 145 A/I system.
