
The maintenance team went to Gavião Peixoto in the EMBRAER Center Service to learn about the activities that they perform in ERJ 145 family and list problems that mechanical find performing the tasks. There the maintenance team had some insights in where they can perform changes to improve the maintenance of the aircraft.

Nowadays EMBRAER's engineering team don't have enough people designing the proposal changes in the ERJ 145 family because it is not the focus of the company anymore. According to EMBRAER's engineers, a simple service bulletin to change a side door to an air stair door takes eight months to be completed.

According to what some of the mentors said, EMBRAER does not provide Supplementary Type Certificates (STC) because many design information are industrial secrets and therefore they can not give some systems designs to other company execute the services. This policy increases the modifications costs since ERJ 145 family operators need to bring they aircrafts to EMBRAER Services Centre to perform the job.

 Another problem is that the facilities that EMBRAER have does not support major system modifications in a ERJ 145 fleet at the same time.
One possible solution is EMBRAER find a partner to perform the STC modifications, leaving to them the costs involving design and implementation.

According to operators, EMBRAER's support is very good, they have a team to help the operator find the solutions for their problems, the only problem is EMBRAER's stored spared parts or, as they call, pool parts, today the pool is located in France, many parts that are need takes at least 15 day to arrive in Brazil.
