
\subsection{Manufacturing}

\subsubsection{Introduction}

The manufacturing team is responsible to give solutions about the strategy of engineering, fabrication and implementation of the proposed changes. These solutions involve trade-off analysis about outsourcing, manufacturing 
locations and implementation. 

This group is also responsible for estimate recurring and non-recurring costs, encompassing engineering, parts manufacturing and implementation.

The following will be presented the strategy to the implementation of the project and the cost estimates.

\subsubsection{Manufacturing Strategies}

This chapter discuss about the make-or-buy decision that covers each project phase, and then a trade-off analysis to determine which strategy is the most interesting to the company.

The make-or-buy decision is very important to control the activities that needs to be done in the house and to direct what kind of suppliers needs to be contacted. In this case it is necessary to consider whether it is 
better to realize the project within the company or outsource the service. It is necessary to analyze some strategic drivers, like old and new partnerships. There are also industrial and commercial drivers: industrial 
capacity, plants occupation and difference between internal and external costs.

To define the strategy the project was divided into five phases, which comprises preliminary project, engineering design, manufacturing, acquisition and implementation. 

The preliminary project is where the requirements are defined and it is being presented in this report. This development will be the responsibility of the EMBRAER, has a development time estimated around 6 months and estimated 
non-recurrent cost around US\$2,000,000.00.

The engineering design is where it is developed the modification to be implemented, including the certification process, and it is realized after the preliminary project. At the end of this stage is issued a Service Bulletin 
(SB) with details of the modification to be implemented in the aircrafts. Analyzing the difference between internal and external costs and the high demand for projects in EMBRAER, it was observed that the best option is to 
outsource and support this service. It is estimated that outsourcing will result in a non-recurrent cost around US\$ 30,000,000.00 and it is expected that this development will last between 8 and 10 months.

The next step is the manufacturing and acquisition of components and tools necessary to implement the change. Along with SB, is provided an engineering order with instructions for manufacturing these components and tools, so 
the operator can hire any workshop to perform the service. It is estimated a recurrent cost around US\$100,000.00 but this value can vary with the operator's contract with the workshop, the quantity and the cadence requested 
by the operator.

While some components need to be manufactured, others can be found in the market. These components must be purchased from certified supliers, or from EMBRAER. There is an estimated recurrent cost around US\$ 750,000.00, 
and the delivery time depends of the availability.

After the components in hand the modification can be implemented in a certified service center, all the change process will be determined in the engineering order. The estimated time to the modification is about 2 months, 
according to the following table:

% Table generated by Excel2LaTeX from sheet 'Plan1'
\begin{table}[htbp]
  \centering
  \caption{Implementation Time}
    \begin{tabular}{rrr}
    \toprule
    \multicolumn{3}{c}{\textbf{Implementation time}} \\
    \midrule
          & \multicolumn{1}{c}{\textbf{Days}} &  \\
    Disassembling & 5     &  \\
    Plug Removal & 10    &  \\
    Plug Installation & 8     &  \\
    Painting / sealing & 6     &  \\
    Systems installation / tests / delivery & 30    &  \\
    \bottomrule
    \end{tabular}%
  \label{tab:imp_time}%
\end{table}%

The estimated recurrent cost to the change implementation is about US\$400,000.00. 

\subsubsection{Conclusion}
With the description presented in the previous section it is possible to observe every stage of the project with each relatives times e costs, are they recurrent or non-recurrent. Although they have been presented separately, 
some of then can occur in parallel and these values can vary according some parameters like: contracts with suppliers, cadence and others like time and place.

The development phase is estimated to last between 14 and 16 months, and includes the preliminar design and the engineering design, that will be elaborated by an outsorced company. The preliminar design was already developed 
and it is presented in this report.

The manufacturing and purchasing phase has costs and times dependents of the operator's process. The implementation will be done according to the operator's logistics and the aircraft availability, this process is estimated 
to last 2 months.
